---
title: "Bicultural identity orientations among Jamaican Canadians"
subtitle: "The sociolinguistic correlates of hybrid, alternating, and conflicting identities in a Creole-using diaspora"
author: "Lars Hinrichs<br/>The University of Texas at Austin"
date: '03/2022'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [xaringan-themer.css, footer-header.css, my-css.css]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---
layout: true
class: middle

<div class="my-footer"><span class="highlight-front">slides: <a href="https://bit.ly/hinrichs-slides-bremen">bit.ly/hinrichs-slides-bremen&emsp;|&emsp;web: <a href="https://larshinrichs.site">larshinrichs.site</a></span></div> 



```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```


```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#480c69",
  secondary_color = "#B8D3B3",
  inverse_header_color = "#FFFFFF",
  header_font_google = google_font("Josefin Sans", "600", "600i"),
  text_font_google   = google_font("Spectral", "300", "300i"),
  text_font_size = "1.8rem",
  title_slide_text_color = "white",
  background_color = "#DCDCDC"
)
```

---
class: inverse

# Outline

1. The Toronto Jamaican Community
1. Bicultural identity orientations
1. Identity orientations in variation analysis
1. Conclusions

---

> Comănaru, Ruxandra-Silvia, Kimberly A. Noels, and Jean-Marc Dewaele. 2018. “Bicultural Identity Orientation of Immigrants to Canada.” *Journal of Multilingual and Multicultural Development* 39:6: 526–41. .small[https://doi.org/10.1080/01434632.2017.1404069]

---

# Bicultural identity orientations

The study design postulated a minimum of three identity orientation types: 
1. integration/hybridity,
1. conflict, and
1. alternation.


---

The researchers remained open to identifying additional orientation types. The initial survey was based on 40 Likert-type items. Results were submitted to a clustering method and the authors determined a __5-cluster model__ was the best fit to the data

---
layout: false

.right.small[Comănaru et al. 2018]

## Five types of bicultural identity orientation

1.	__conflicted__ &mdash; a perceived discord between the two cultural identities
--

1.	__monocultural__ &mdash;	identification with only one of the two cultures
--

1.	__alternating__ &mdash;	the shifting of identities according to the cultural context)
--

1.	__complementary__ &mdash;	compatibility between the two distinct identities), and
--

1.	__hybrid__ &mdash;	the blending of two cultural identities, yielding a new identity

---



